partial: An R Package for Creating Partial Dependence Plots

### 2016-09-01 manuscript/greenwell.tex
minor edits

Currently supported models are described in Table~\ref{tab:models}. Using the \code{partial.default} method it is still possible to handle many other models not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package. However, for these cases, the user will need to specify additional options in the call to \code{partial}.

@@

>>>>

Currently supported models are described in Table~\ref{tab:models}. Using the \code{partial.default} method it is still possible to handle many other models not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package. However, for these cases, the user will need to specify the additional options \code{super.type} (i.e., \code{"regression"} or \code{"classification"}) and \code{train} (the original training data) in the call to \code{partial}---the exception in Table~\ref{tab:models} is using partial with \code{"xgb.Booster"} models, which requires the user to specify \code{train}.

@@

Finally, for further illustration, we will compare the random forest results with those obtained from gradient boosting; for this, we shal use the popular \pkg{xgboost} package. The example below, uses \pkg{xgboost} to model the boston housing data. The tuning parameters were predetermined using 5-fold cross-validation.
\begin{example}
set.seed(102)
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv,
                      objective = "reg:linear",
                      nrounds = 2000,
                      max_depth = 3,
                      eta = 0.01)
\end{example}

To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response!) in the call to \code{partial}:
\begin{example}
partial(boston.xgb, pred.var = "lstat", train = subset(boston, select = -cmedv), 
        plot = TRUE)
\end{example}
